Manuscript_Github_Pchabaudi_qusage

### 2022-08-28 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_qusage.Rmd
Look at L4s ChAPL and AAPLs separate

@@

all_comparisons <- lapply(comparisons_stagesTrans, 
                          function(comparison){
                            print(comparison)
                            list_comp <- lapply(
                              list(pir_geneset,
                                   ShortLong_list,
                                   subfam_list,
                                   locus_list), 
                              function(gene_list){
                                qs.results.subfam <- qusage(comp_stagesTrans.mat,
                                                            lifeCycle_labels,
                                                            comparison,
                                                            gene_list,
                                                            n.points = 2^18)
                                list(results = qs.results.subfam, 
                                     qstable = qsTable(qs.results.subfam) %>% 
                                       mutate(contrast = qs.results.subfam$contrast))
                              })
                            names(list_comp) <- c('pir', 'shortlong', 'subfam', 'locus')
                            list_comp$combined <- bind_rows(lapply(list_comp, 
                                                                   getElement, 
                                                                   'qstable'))
                            return(list_comp)
                          })
names(all_comparisons) <- comparisons_stagesTrans

@@

all_comparisons_transStage <- 
  lapply(c('rMT', 'SBP'), 
         function(transmission){
           #Extract the comparisons for this transmission method
           comparisons_transStage <- comparisons_transStage.list[[transmission]]
           #Subset the dataset based on the transmission and removing sch.cultures
           comp_transStage.mat <- chab_tpm_log2plus1.mat[
             ,str_detect(colnames(chab_tpm_log2plus1.mat), pattern = paste0(transmission,'_(?!sch.culture)'))
           ]
           #Get appropriate life cycle labels from this.
           lifeCycle_labels <- str_extract(colnames(comp_transStage.mat),
                                pattern = '^(rMT|SBP)_([[:digit:]]{2}h|sch.culture)')
           results_transStage.list <- lapply(comparisons_transStage, 
                  function(comparison){
                    print(comparison)
                    list_comp <- lapply(
                      list(pir_geneset,
                           ShortLong_list,
                           subfam_list,
                           locus_list), 
                      function(gene_list){
                        print(deparse(substitute(gene_list)))
                        qs.results.subfam <- qusage(comp_transStage.mat,
                                                    lifeCycle_labels,
                                                    comparison,
                                                    gene_list,
                                                    n.points = 2^18)
                        list(results = qs.results.subfam, 
                             qstable = qsTable(qs.results.subfam) %>% 
                               mutate(contrast = qs.results.subfam$contrast))
                      })
                    names(list_comp) <- c('pir', 'shortlong', 'subfam', 'locus')
                    list_comp$combined <- bind_rows(lapply(list_comp, 
                                                           getElement, 
                                                           'qstable'))
                    return(list_comp)
                  })
           names(results_transStage.list) <- comparisons_transStage
           return(results_transStage.list)
         })
names(all_comparisons_transStage) <- c('rMT', 'SBP')

>>>>

cir_info <- mutate(cir_info, 
                   subfam_loci = paste(subfam,
                                       chapl_aapl, 
                                       sep = '_'))
L4_loci_list <- lapply(c('L4_ChAPL', 'L4_AAPL'), 
                  function(clade_nam) filter(cir_info, 
                                             subfam_loci == clade_nam)$Geneid)
names(L4_loci_list) <- c('L4_ChAPL', 'L4_AAPL')
L4_loci_list <- L4_loci_list[unlist(lapply(L4_loci_list, 
                                         function(x) length(x) > 3))]

@@

all_comparisons <- lapply(comparisons_stagesTrans, 
                          function(comparison){
                            print(comparison)
                            list_comp <- lapply(
                              list(pir_geneset,
                                   ShortLong_list,
                                   subfam_list,
                                   L4_loci_list,
                                   locus_list), 
                              function(gene_list){
                                qs.results.subfam <- qusage(comp_stagesTrans.mat,
                                                            lifeCycle_labels,
                                                            comparison,
                                                            gene_list,
                                                            n.points = 2^18)
                                list(results = qs.results.subfam, 
                                     qstable = qsTable(qs.results.subfam) %>% 
                                       mutate(contrast = qs.results.subfam$contrast))
                              })
                            names(list_comp) <- c('pir', 'shortlong', 'subfam', 'locus')
                            list_comp$combined <- bind_rows(lapply(list_comp, 
                                                                   getElement, 
                                                                   'qstable'))
                            return(list_comp)
                          })
names(all_comparisons) <- comparisons_stagesTrans

@@

all_comparisons_transStage <- 
  lapply(c('rMT', 'SBP'), 
         function(transmission){
           #Extract the comparisons for this transmission method
           comparisons_transStage <- comparisons_transStage.list[[transmission]]
           #Subset the dataset based on the transmission and removing sch.cultures
           comp_transStage.mat <- chab_tpm_log2plus1.mat[
             ,str_detect(colnames(chab_tpm_log2plus1.mat), pattern = paste0(transmission,'_(?!sch.culture)'))
           ]
           #Get appropriate life cycle labels from this.
           lifeCycle_labels <- str_extract(colnames(comp_transStage.mat),
                                pattern = '^(rMT|SBP)_([[:digit:]]{2}h|sch.culture)')
           results_transStage.list <- lapply(comparisons_transStage, 
                  function(comparison){
                    print(comparison)
                    list_comp <- lapply(
                      list(pir_geneset,
                           ShortLong_list,
                           subfam_list,
                           L4_loci_list,
                           locus_list), 
                      function(gene_list){
                        qs.results.subfam <- qusage(comp_transStage.mat,
                                                    lifeCycle_labels,
                                                    comparison,
                                                    gene_list,
                                                    n.points = 2^18)
                        list(results = qs.results.subfam, 
                             qstable = qsTable(qs.results.subfam) %>% 
                               mutate(contrast = qs.results.subfam$contrast))
                      })
                    names(list_comp) <- c('pir', 'shortlong', 'subfam', 'locus')
                    list_comp$combined <- bind_rows(lapply(list_comp, 
                                                           getElement, 
                                                           'qstable'))
                    return(list_comp)
                  })
           names(results_transStage.list) <- comparisons_transStage
           return(results_transStage.list)
         })
names(all_comparisons_transStage) <- c('rMT', 'SBP')
